Quantitative Auditing of AI Fairness with Differentially Private Synthetic Data

### 2024-12-17 paper/paper.tex
Conclusion

>>>>

In the delicate dialectic of fairness and privacy, auditing AI models with real data can be dangerous. Our work explores a new terrain yet to be touched. By leveraging differentially private synthetic data, our proposed framework for fairness auditing offers a refuge from the vulnerabilities of using real data.

Empirical trials across multiple datasets reveal that synthetic data derived from real data remain sufficiently intact to serve as instruments of audit. However, evaluating the formulas, we also find some measures betray the inherent imperfection of the synthetic approach, and their error margin corroborates our stipulation.

Auditors are, thus, in our new framework, equipped with a new tool that tempers risk at the cost of nuance. Synthetic data, imperfect as it is, emerges as a pragmatic ally, preserving enough fairness properties and auditing utility without sacrificing the sanctuary of privacy.
